---
date: 'Report generated `r format(Sys.time(), "%A, %B %d, %Y")`'
output:
 html_document:
  toc: TRUE
  toc_float: TRUE
params:
   country: "Brazil"
   pre_period_start: '2004-01-01'
   period_period_end: '2009-12-31'
   post_period_start: '2010-01-01'
   post_period_end: '2013-12-01'
   eval_period_start: '2012-01-01' 
   eval_period_end: '2013-12-01'
   year_def: 'cal_year'
   sensitivity: TRUE
   crossval: TRUE
   group_name: 'age_group'
   date_name: 'date'
   outcome_name: 'J12_18'  
   denom_name: 'ach_noj' 
   n_seasons: 12
   input_directory: 'https://raw.githubusercontent.com/weinbergerlab/synthetic-control/master/Datasets%20for%20PNAS/'
   file_name: "Dataset%20S1%20Brazil.csv"
   github.import: TRUE 
   update_packages: FALSE 
   install_packages: TRUE 
---

---
title: "Estimated change associated with the introduction of vaccine in `r params$country`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE, warnings = FALSE)
```

```{r specify_inputs, include=FALSE}
#MOST DATES MUST BE IN FORMAT "YYYY-MM-01", exception is end of pre period, which is 1 day before end of post period
pre_period        <- as.Date(c( params$pre_period_start, params$pre_period_end)) #Range over which the data is trained for the CausalImpact model.
start_date<-        pre_period[1]
post_period       <- as.Date(c(params$post_period_start,params$post_period_end )) #Range from the intervention date to the end date.
intervention_date <- post_period[1]-1
end_date          <- post_period[2]

eval_period       <- as.Date(c(params$eval_period_start, params$eval_period_end)) #Range over which rate ratio calculation will be performed.
year_def   <- params$year_def  #Can be cal_year to aggregate results by Jan-Dec; 'epi_year' to aggregate July-June
sensitivity=params$sensitivity
crossval=params$crossval #run cross validation? Note this takes time...adds ~40 min with 10 age groups, 7 cores
group_name   <- params$group_name #Name of column containing group labels.
date_name    <- params$date_name     #Name of column containing dates.
outcome_name <- params$outcome_name    #Name of column containing outcome.
denom_name   <- params$denom_name   #Name of column containing denominator to be used in offset.
  update_packages  <- params$update_packages 
  install_packages <- params$install_packages 
  install_pandoc   <- FALSE
```

```{r load_packages, include = FALSE}

packages <- c('knitr','parallel','RCurl' ,'pomp','splines', 'MASS','lubridate','loo', 'RcppRoll','lme4', 'ggplot2', 'reshape','dummies')
packageHandler(packages, update_packages, install_packages)
sapply(packages, library, quietly = TRUE, character.only = TRUE)

#Detect if pogit package installed; if not download from Github
if("pogit" %in% rownames(installed.packages())==FALSE){
  if("devtools" %in% rownames(installed.packages())==FALSE){
    install.packages('devtools')
  }
  library('devtools')
  install_github("airbornemint/pogit") #Did not update any of the dependencies (#24)
}
library(pogit)
```

```{r setup_data, include=FALSE}

###WORKING DIRECTORY Should be set as the directory where .Rmd file is saved  ####
#setwd(auto.wd) ##automatically set working directory to '~desktop/synthetic-control-poisson-master/main analysis components/'
#setwd('C:/Users/dmw63/Documents/GitHub/synthetic-control-poisson/main analysis components')

#Assign variable values
country       <- params$country #Country or region name.
n_seasons     <- params$n_seasons       #Number of months (seasons) per year. 12 for monthly, 4 for quarterly, 3 for trimester data.
exclude_covar <- c()      #User-defined list of covariate columns to exclude from all analyses.
exclude_group <- c()      #User-defined list of groups to exclude from analyses.
if(country=="Brazil"){code_change   <- TRUE     #Used for Brazil data. Set to TRUE to adjust for year 2008 coding changes; otherwise, set to FALSE.
    }else{
    code_change   <- FALSE
  }

input_directory  <-params$input_directory
file_name=params$file_name
output_directory <- '../Results'   #Directory where results will be saved.
output_directory <- paste(output_directory,'_',params$country,'_', format(Sys.time(), '%Y-%m-%d-%H%M%S'), '/', sep = '')                     #Adds a subfolder to output directory to organize results by date and time run.
dir.create(output_directory, recursive = TRUE, showWarnings = FALSE)

data_file <- paste0(input_directory, file_name)
if(params$github.import==FALSE){
prelog_data <- read.csv(data_file, check.names = FALSE)# IF IMPORTING FROM LOCAL
}else{
prelog_data <- read.csv(text=getURL(data_file), check.names = FALSE)# IF IMPORTING FROM URL
}
prelog_data<-prelog_data[!is.na(prelog_data[,outcome_name]),]#If outcome is missing, delete 
groups <- as.character(unique(unlist(prelog_data[, group_name], use.names = FALSE)))
if (exists('exclude_group')) {groups <- groups[!(groups %in% exclude_group)]}


#How many cores for parallel processing steps?
n_cores <- detectCores()
set.seed(1)
```


```{r format_covars, include = FALSE}
prelog_data[,date_name]<-as.Date(as.character(prelog_data[,date_name]), tryFormats=c("%m/%d/%Y",'%Y-%m-%d' ))

#test<-split(prelog_data, factor(prelog_data[,group_name]))
#outcome.na<-sapply(test, function(x) sum(is.na(x[,outcome_name])))
prelog_data[, date_name] <- formatDate(prelog_data[, date_name])
prelog_data <- setNames(lapply(groups, FUN = splitGroup, ungrouped_data = prelog_data, group_name = group_name, date_name = date_name, start_date = start_date, end_date = end_date, no_filter = c(group_name, date_name, outcome_name, denom_name)), groups)
#if (exists('exclude_group')) {prelog_data <- prelog_data[!(names(prelog_data) %in% exclude_group)]}

#Log-transform all variables, adding 0.5 to counts of 0.
ds <- setNames(lapply(prelog_data, FUN = logTransform, no_log = c(group_name, date_name,outcome_name)), groups)
time_points <- unique(ds[[1]][, date_name])
print(3)

#Monthly dummies
if(n_seasons==4){dt<-quarter(as.Date(time_points))}
if(n_seasons==12){dt<-month(as.Date(time_points))}
if(n_seasons==3){
  dt.m<-month(as.Date(time_points))
  dt<-dt.m
  dt[dt.m %in% c(1,2,3,4)]<-1
  dt[dt.m %in% c(5,6,7,8)]<-2
  dt[dt.m %in% c(9,10,11,12)]<-3
    }
season.dummies<-dummies::dummy(dt)
season.dummies<-as.data.frame(season.dummies)
names(season.dummies)<-paste0('s', 1:n_seasons)
season.dummies<-season.dummies[,-n_seasons]
print(4)

ds <- lapply(ds, function(ds) {
	if (!(denom_name %in% colnames(ds))) {
		ds[denom_name] <- 0
	}
	return(ds)
})
print(5)

sparse_groups <- sapply(ds, function(ds) {
	return(ncol(ds[!(colnames(ds) %in% c(date_name, group_name, denom_name, outcome_name, exclude_covar))]) == 0)
})
ds <- ds[!sparse_groups]
groups <- groups[!sparse_groups]

#Process and standardize the covariates. For the Brazil data, adjust for 2008 coding change.
covars_full <- setNames(lapply(ds, makeCovars), groups)
covars_full <- lapply(covars_full, FUN = function(covars) {covars[, !(colnames(covars) %in% exclude_covar), drop = FALSE]})
covars_time <- setNames(lapply(covars_full, FUN = function(covars) {as.data.frame(list(cbind(season.dummies,time_index = 1:nrow(covars))))}), groups)
covars_null <- setNames(lapply(covars_full, FUN = function(covars) {as.data.frame(list(cbind(season.dummies)))}), groups)
print(6)

#Standardize the outcome variable and save the original mean and SD for later analysis.
outcome      <- sapply(ds, FUN = function(data) {data[, outcome_name]})
outcome_plot=outcome
offset<- sapply(ds, FUN=function(data) exp(data[, denom_name]) )  #offset term on original scale; 1 column per age group

```

```{r stl_pca , include = FALSE}
##SECTION 1: CREATING SMOOTHED VERSIONS OF CONTROL TIME SERIES AND APPENDING THEM ONTO ORIGINAL DATAFRAME OF CONTROLS
#EXTRACT LONG TERM TREND WITH DIFFERENT LEVELS OF SMOOTHNESS USING STL
# Set a list of parameters for STL
stl.covars<-mapply(smooth_func,ds.list=ds,covar.list=covars_full, SIMPLIFY=FALSE) 
post.start.index<-which(time_points==post_period[1])

if (length(groups)>1){ 
  stl.data.setup<-mapply(stl_data_fun,covars=stl.covars, ds.sub=ds ,SIMPLIFY=FALSE)  #list of lists that has covariates for each regression for each strata
}else{
  stl.data.setup <- list(mapply(stl_data_fun,covars=stl.covars, ds.sub=ds ))
}

##SECTION 2: run first stage models
n_cores <- detectCores()-1
glm.results<- vector("list",  length=length(stl.data.setup)) #combine models into a list
cl1 <- makeCluster(n_cores)
clusterEvalQ(cl1, {library(lme4, quietly = TRUE)})
clusterExport(cl1, c('stl.data.setup',  'glm.fun', 'time_points', 'n_seasons','post.start.index'), environment())
for(i in 1:length(stl.data.setup)){
  print(i)
  glm.results[[i]]<-parLapply(cl=cl1 ,     stl.data.setup[[i]], fun=glm.fun )
}
stopCluster(cl1)
######################
```

```{r combine_data, include = FALSE}
#Combine the outcome, covariates, and time point information.
data_full <- setNames(lapply(groups, makeTimeSeries, outcome = outcome,       covars = covars_full), groups)
data_time <- setNames(lapply(groups, makeTimeSeries, outcome = outcome, covars = covars_time, trend=TRUE), groups)
data_pca<-mapply(FUN=pca_top_var,glm.results.in=glm.results, covars=stl.covars,ds.in=ds, SIMPLIFY=FALSE)
names(data_pca)<-groups
#Null model where we only include seasonal terms but no covariates
data_null <- setNames(lapply(groups, makeTimeSeries, outcome = outcome, covars = covars_null, trend=FALSE), groups)
#Time trend model but without a denominator
data_time_no_offset <- setNames(lapply(groups, makeTimeSeries, outcome = outcome, covars = covars_time, trend=FALSE), groups)
```


```{r main analysis, include = FALSE}

#Start Cluster for CausalImpact (the main analysis function).
cl <- makeCluster(n_cores)
clusterEvalQ(cl, {library(pogit, quietly = TRUE); library(lubridate, quietly = TRUE)})
clusterExport(cl, c('doCausalImpact',  'intervention_date', 'time_points', 'n_seasons','crossval'), environment())
impact_full <- setNames(parLapply(cl, data_full, doCausalImpact, intervention_date = intervention_date, var.select.on=TRUE, time_points = time_points), groups)
impact_time <- setNames(parLapply(cl, data_time, doCausalImpact, intervention_date = intervention_date,  var.select.on=FALSE,time_points = time_points, trend = TRUE), groups)
impact_time_no_offset <- setNames(parLapply(cl, data_time_no_offset, doCausalImpact, intervention_date = intervention_date,  var.select.on=FALSE,time_points = time_points,  trend = FALSE), groups)
impact_pca <- setNames(parLapply(cl, data_pca, doCausalImpact, intervention_date = intervention_date, var.select.on=FALSE, time_points = time_points), groups)
#No covariates, but with random intercept
#impact_seas_only <- setNames(parLapply(cl, data_null, doCausalImpact, intervention_date = intervention_date, var.select.on=FALSE, time_points = time_points, n_seasons = n_seasons), groups)
#No covariates except seasonal, no random intercept
#impact_seas_only_no_re <- setNames(parLapply(cl, data_null, doCausalImpact, intervention_date = intervention_date, var.select.on=FALSE,ri.select=FALSE, time_points = time_points, n_seasons = n_seasons), groups)
stopCluster(cl)
```

```{r crossval, include = FALSE}
  if(crossval){
      #Creates List of lists: 1 entry for each stratum; within this, there are CV datasets for each year left out, and within this, there are 2 lists, one with full dataset, and one with the CV dataset
        cv.data_full<-lapply(data_full, makeCV)
        cv.data_time<-lapply(data_time, makeCV)
        cv.data_time_no_offset<-lapply(data_time_no_offset, makeCV)
        cv.data_pca<-lapply(data_pca, makeCV)
      #zoo_data<-cv.data_time[[1]][[2]]
      #Run the models on each of these datasets
        # Start the clock!--takes ~45 minutes
          ptm <- proc.time()
        cl <- makeCluster(n_cores)
        clusterEvalQ(cl, {library(pogit, quietly = TRUE); library(lubridate, quietly = TRUE)})
        clusterExport(cl, c('doCausalImpact',  'intervention_date', 'time_points', 'n_seasons','crossval'), environment())
          cv_impact_full <-setNames(parLapply(cl, cv.data_full, function(x) lapply(x, doCausalImpact,crossval.stage=TRUE, intervention_date = intervention_date,  var.select.on=TRUE, time_points = time_points)), groups)
          cv_impact_time_no_offset <-setNames(parLapply(cl, cv.data_time_no_offset, function(x) lapply(x, doCausalImpact,crossval.stage=TRUE, trend=FALSE, intervention_date = intervention_date,  var.select.on=FALSE, time_points = time_points)), groups)
          cv_impact_time <-setNames(parLapply(cl, cv.data_time, function(x) lapply(x, doCausalImpact,crossval.stage=TRUE, trend=TRUE, intervention_date = intervention_date,  var.select.on=FALSE, time_points = time_points)), groups)
          cv_impact_pca <-setNames(parLapply(cl, cv.data_pca, function(x) lapply(x, doCausalImpact,crossval.stage=TRUE, intervention_date = intervention_date,  var.select.on=FALSE, time_points = time_points)), groups)
        stopCluster(cl)
        # Stop the clock
        proc.time() - ptm
      
        #Calculate pointwise log likelihood for cross-val prediction sample vs observed
        #These are N_iter*N_obs*N_cross_val array
        ll.cv.full<-lapply(cv_impact_full, function(x) lapply(x,crossval.log.lik))
        ll.cv.full2<-lapply(ll.cv.full, reshape.arr)
        #
        ll.cv.time_no_offset<-lapply(cv_impact_time_no_offset, function(x) lapply(x,crossval.log.lik))
        ll.cv.time_no_offset2<-lapply(ll.cv.time_no_offset, reshape.arr)
        #
        ll.cv.time<-lapply(cv_impact_time, function(x) lapply(x,crossval.log.lik))
        ll.cv.time2<-lapply(ll.cv.time, reshape.arr)
        #
        ll.cv.pca<-lapply(cv_impact_pca, function(x) lapply(x,crossval.log.lik))
        ll.cv.pca2<-lapply(ll.cv.pca, reshape.arr)
        #Create list that has model result for each stratum
        ll.compare<- vector("list", length(ll.cv.pca2)) 
      stacking_weights.all<-matrix(NA, nrow=length(ll.cv.pca2), ncol=4)
        
         for(i in 1:length(ll.compare)){
          ll.compare[[i]]<-cbind(ll.cv.full2[[i]],ll.cv.time_no_offset2[[i]],ll.cv.time2[[i]],ll.cv.pca2[[i]])#will get NAs if one of covariates is constant in fitting period (ie pandemic flu dummy)...shoud=ld fix this above
          keep<-complete.cases(ll.compare[[i]])
          ll.compare[[i]]<-ll.compare[[i]][keep,]
          #occasionally if there is a very poor fit, likelihood is very very small, which leads to underflow issue and log(0)...delete these rows to avoid this as a dirty solution. Better would be to fix underflow
          row.min<-apply(exp(ll.compare[[i]]),1,min)
          ll.compare[[i]]<-ll.compare[[i]][!(row.min==0),]
          #if(min(exp(ll.compare[[i]]))>0){
             stacking_weights.all[i,]<-stacking_weights(ll.compare[[i]])
           #}
         }
      stacking_weights.all<-as.data.frame(round(stacking_weights.all,3))
        names(stacking_weights.all)<-c('Synthetic Controls', 'Time trend', 'Time trend (no offset)', 'STL+PCA')
        stacking_weights.all<-cbind.data.frame(groups,stacking_weights.all)
        stacking_weights.all.m<-melt(stacking_weights.all, id.vars='groups')
       # stacking_weights.all.m<-stacking_weights.all.m[order(stacking_weights.all.m$groups),]
        
        stacked.ests<-mapply(  FUN=stack.mean,group=groups,impact_full=impact_full,impact_time=impact_time,impact_time_no_offset=impact_time_no_offset,impact_pca=impact_pca, SIMPLIFY=FALSE )
       # plot.stacked.ests<-lapply(stacked.ests,plot.stack.est)
        quantiles_stack <- setNames(lapply(groups, FUN = function(group) {rrPredQuantiles(impact = stacked.ests[[group]], denom_data = ds[[group]][, denom_name],        eval_period = eval_period, post_period = post_period)}), groups)
        pred_quantiles_stack <- sapply(quantiles_stack, getPred, simplify = 'array')
        rr_roll_stack <- sapply(quantiles_stack, FUN = function(quantiles_stack) {quantiles_stack$roll_rr}, simplify = 'array')
        rr_mean_stack <- round(t(sapply(quantiles_stack, getRR)),2)
        rr_mean_stack_intervals <- data.frame('Stacking Estimate (95% CI)'     = makeInterval(rr_mean_stack[, 2], rr_mean_stack[, 3], rr_mean_stack[, 1]), check.names = FALSE, row.names = groups)
        cumsum_prevented_stack <- sapply(groups, FUN = cumsum_func, quantiles = quantiles_stack, simplify = 'array')
        ann_pred_quantiles_stack <- sapply(quantiles_stack, getAnnPred, simplify = FALSE)
        
        #Preds: Compare observed and expected
        pred.cv.full<-lapply(cv_impact_full, function(x) sapply(x,pred.cv,simplify='array'))
        pred.cv.pca<-lapply(cv_impact_pca, function(x) sapply(x,pred.cv,simplify='array'))
          
        # # par(mfrow=c(3,2))
        # plot.grp=9
        # for(i in 1:6){
        # matplot(pred.cv.full[[plot.grp]][,c(2:4),i], type='l', ylab='Count',col='#1b9e77', lty=c(2,1,2), bty='l', ylim=range(pred.cv.full[[plot.grp]][,c(1),i])*c(0.8,1.2))
        # points(pred.cv.full[[plot.grp]][,c(1),i], pch=16)
        # title("Synthetic controls: Cross validation")
        # matplot(pred.cv.pca[[plot.grp]][,c(2:4),i], type='l',ylab='Count', col='#d95f02', lty=c(2,1,2), bty='l', ylim=range(pred.cv.full[[plot.grp]][,c(1),i])*c(0.8,1.2))
        # points(pred.cv.pca[[plot.grp]][,c(1),i], pch=16)
        # title("STL+PCA: Cross validation")
        # }
        
        save.stack.est<-list(post_period,outcome_plot, time_points,ann_pred_quantiles_stack, pred_quantiles_stack,rr_roll_stack,rr_mean_stack,rr_mean_stack_intervals,cumsum_prevented_stack)
        names(save.stack.est)<-c('post_period','outcome_plot','time_points', 'ann_pred_quantiles_stack', 'pred_quantiles_stack','rr_roll_stack','rr_mean_stack','rr_mean_stack_intervals','cumsum_prevented_stack')
        saveRDS(save.stack.est, file=paste0(output_directory, country, "Stack estimates.rds"))
        
        #Pointwise RR and uncertainty for second stage meta analysis
        log_rr_quantiles_stack   <- sapply(quantiles_stack,   FUN = function(quantiles) {quantiles$log_rr_full_t_quantiles}, simplify = 'array')
        dimnames(log_rr_quantiles_stack)[[1]] <- time_points
        log_rr_full_t_samples.stack.prec<-sapply(quantiles_stack,   FUN = function(quantiles) {quantiles$log_rr_full_t_samples.prec.post}, simplify = 'array')
        #log_rr_sd.stack   <- sapply(quantiles_stack,   FUN = function(quantiles) {quantiles$log_rr_full_t_sd}, simplify = 'array')
        
        saveRDS(log_rr_quantiles_stack, file=paste0(output_directory, country, "_log_rr_quantiles_stack.rds"))
        saveRDS(log_rr_full_t_samples.stack.prec, file=paste0(output_directory, country, "_log_rr_full_t_samples.stack.prec.rds"))
      }
```

```{r format_save_results, include = FALSE}

#Save the inclusion probabilities from each of the models
inclusion_prob_full <- setNames(lapply(impact_full, inclusionProb), groups)
inclusion_prob_time <- setNames(lapply(impact_time, inclusionProb), groups)

model.size.sc<-sapply(impact_full,modelsize_func)

#All model results combined
quantiles_full <- setNames(lapply(groups, FUN = function(group) {rrPredQuantiles(impact = impact_full[[group]], denom_data = ds[[group]][, denom_name],        eval_period = eval_period, post_period = post_period)}), groups)
quantiles_time <- setNames(lapply(groups, FUN = function(group) {rrPredQuantiles(impact = impact_time[[group]], denom_data = ds[[group]][, denom_name],  eval_period = eval_period, post_period = post_period)}), groups)
quantiles_time_no_offset <- setNames(lapply(groups, FUN = function(group) {rrPredQuantiles(impact = impact_time_no_offset[[group]], denom_data = ds[[group]][, denom_name],  eval_period = eval_period, post_period = post_period)}), groups)
quantiles_pca <- setNames(lapply(groups, FUN = function(group) {rrPredQuantiles(impact = impact_pca[[group]], denom_data = ds[[group]][, denom_name],        eval_period = eval_period, post_period = post_period)}), groups)
quantiles_best<-vector("list", length(quantiles_full)) 
quantiles_best[model.size.sc>=1]<-quantiles_full[model.size.sc>=1]
quantiles_best[model.size.sc<1]<-quantiles_pca[model.size.sc<1]
quantiles_best<-setNames(quantiles_best,groups)


#Model predicitons
pred_quantiles_full <- sapply(quantiles_full, getPred, simplify = 'array')
pred_quantiles_time <- sapply(quantiles_time, getPred, simplify = 'array')
pred_quantiles_time_no_offset <- sapply(quantiles_time_no_offset, getPred, simplify = 'array')
pred_quantiles_pca <- sapply(quantiles_pca, getPred, simplify = 'array')
pred_quantiles_best <- sapply(quantiles_best, getPred, simplify = 'array')

#Predictions, aggregated by year
ann_pred_quantiles_full <- sapply(quantiles_full, getAnnPred, simplify = FALSE)
ann_pred_quantiles_time <- sapply(quantiles_time, getAnnPred, simplify = FALSE)
ann_pred_quantiles_time_no_offset <- sapply(quantiles_time_no_offset, getAnnPred, simplify = FALSE)
ann_pred_quantiles_pca <- sapply(quantiles_pca, getAnnPred, simplify = FALSE)
ann_pred_quantiles_best<-sapply(quantiles_best, getAnnPred, simplify = FALSE)

#Pointwise RR and uncertainty for second stage meta analysis
log_rr_quantiles   <- sapply(quantiles_full,   FUN = function(quantiles) {quantiles$log_rr_full_t_quantiles}, simplify = 'array')
dimnames(log_rr_quantiles)[[1]] <- time_points
log_rr_sd   <- sapply(quantiles_full,   FUN = function(quantiles) {quantiles$log_rr_full_t_sd}, simplify = 'array')
log_rr_full_t_samples.prec<-sapply(quantiles_full,   FUN = function(quantiles) {quantiles$log_rr_full_t_samples.prec}, simplify = 'array')
saveRDS(log_rr_quantiles, file=paste0(output_directory, country, "_log_rr_quantiles.rds"))
saveRDS(log_rr_sd, file=paste0(output_directory, country, "_log_rr_sd.rds"))
saveRDS(log_rr_full_t_samples.prec, file=paste0(output_directory, country, "_log_rr_full_t_samples.prec.rds"))

log_rr_quantiles_best   <- sapply(quantiles_best,   FUN = function(quantiles) {quantiles$log_rr_full_t_quantiles}, simplify = 'array')
dimnames(log_rr_quantiles_best)[[1]] <- time_points
log_rr_best_t_samples.prec<-sapply(quantiles_best,   FUN = function(quantiles) {quantiles$log_rr_full_t_samples.prec}, simplify = 'array')
saveRDS(log_rr_quantiles_best, file=paste0(output_directory, country, "_log_rr_quantiles_best.rds"))
saveRDS(log_rr_best_t_samples.prec, file=paste0(output_directory, country, "_log_rr_best_t_samples.prec.rds"))

#Rolling rate ratios
rr_roll_full <- sapply(quantiles_full, FUN = function(quantiles_full) {quantiles_full$roll_rr}, simplify = 'array')
rr_roll_time <- sapply(quantiles_time, FUN = function(quantiles_time) {quantiles_time$roll_rr}, simplify = 'array')
rr_roll_time_no_offset <- sapply(quantiles_time_no_offset, FUN = function(quantiles_time) {quantiles_time$roll_rr}, simplify = 'array')
rr_roll_pca <- sapply(quantiles_pca, FUN = function(quantiles_pca) {quantiles_pca$roll_rr}, simplify = 'array')
rr_roll_best <- sapply(quantiles_best, FUN = function(quantiles_best) {quantiles_best$roll_rr}, simplify = 'array')

#Rate ratios for evaluation period.

rr_mean_full <- t(sapply(quantiles_full, getRR))
rr_mean_time <- t(sapply(quantiles_time, getRR))
rr_mean_time_no_offset <- t(sapply(quantiles_time_no_offset, getRR))
rr_mean_pca <- t(sapply(quantiles_pca, getRR))
rr_mean_best <- t(sapply(quantiles_best, getRR))


rr_mean_best  <- t(sapply(quantiles_best, getRR))
log_rr_sd_best  <- t(sapply(quantiles_best, getsdRR))
 			    
			    
rr_mean_full_intervals <- data.frame('SC Estimate (95% CI)'     = makeInterval(rr_mean_full[, 2], rr_mean_full[, 3], rr_mean_full[, 1]), check.names = FALSE, row.names = groups)
rr_mean_time_intervals <- data.frame('Time trend Estimate (95% CI)' = makeInterval(rr_mean_time[, 2], rr_mean_time[, 3], rr_mean_time[, 1]), check.names = FALSE, row.names = groups)
rr_mean_time_no_offset_intervals <- data.frame('Time trend (no offset) Estimate (95% CI)' = makeInterval(rr_mean_time_no_offset[, 2], rr_mean_time_no_offset[, 3], rr_mean_time_no_offset[, 1]), check.names = FALSE, row.names = groups)
rr_mean_pca_intervals <- data.frame('STL+PCA Estimate (95% CI)'     = makeInterval(rr_mean_pca[, 2], rr_mean_pca[, 3], rr_mean_pca[, 1]), check.names = FALSE, row.names = groups)
rr_mean_best_intervals <- data.frame('Best Estimate (95% CI)'     = makeInterval(rr_mean_best[, 2], rr_mean_best[, 3], rr_mean_best[, 1]), check.names = FALSE, row.names = groups)
#rr_mean_best_intervals <- data.frame('Best Unbiased Estimate (95% CI)'     = makeInterval(rr_mean_best_unbias[, 2], rr_mean_best_unbias[, 3], rr_mean_best_unbias[, 1]), check.names = FALSE, row.names = groups)

colnames(rr_mean_time) <- paste('Time_trend', colnames(rr_mean_time))
rr_mean_best_intervals <- data.frame('Best Estimate (95% CI)'     = makeInterval(rr_mean_best[, 2], rr_mean_best[, 3], rr_mean_best[, 1]), check.names = FALSE, row.names = groups)

			    
#Run a classic ITS analysis and save output (rr at last time point) as .csv
rr.its1<-lapply(data_time,its_func)
rr.t<-sapply(rr.its1, `[[`, "rr.q.t", simplify='array')
rr.end<-t(sapply(rr.its1, `[[`, "rr.q.post", simplify='array')) 
#matplot(rr.t[,,10], bty='l', type='l', lty=c(2,1,2), col='gray')
#abline(h=1)
write.csv(rr.end, paste(output_directory, country, 'rr_classic_its.csv', sep = ''))
rr_mean_its_intervals <- data.frame('Classic ITS (95% CI)'     = makeInterval(rr.end[, 2], rr.end[, 3], rr.end[, 1]), check.names = FALSE, row.names = groups)

#Combine RRs into 1 file for plotting
rr_mean_combo<- as.data.frame(rbind( cbind(rep(1, nrow(rr_mean_full)),groups,  seq(from=1, by=1, length.out=nrow(rr_mean_full)),rr_mean_full),
                       cbind(rep(2, nrow(rr_mean_time)),groups, seq(from=1, by=1, length.out=nrow(rr_mean_full)), rr_mean_time),
                       cbind(rep(3, nrow(rr_mean_time_no_offset)),groups, seq(from=1, by=1, length.out=nrow(rr_mean_full)), rr_mean_time_no_offset),
                    cbind(rep(4, nrow(rr_mean_pca)), groups, seq(from=1, by=1, length.out=nrow(rr_mean_full)),rr_mean_pca)))
        names(rr_mean_combo)<-c('Model', 'groups', 'group.index','lcl','mean.rr','ucl')
        if(crossval){
          point.weights2<-stacking_weights.all.m
        }else{
          point.weights2<-as.data.frame(matrix(rep(1,nrow(rr_mean_combo)), ncol=1))
          names(point.weights2)<-'value'
        }
        rr_mean_combo$point.weights<-point.weights2$value
        rr_mean_combo$group.index<-as.numeric(as.character(rr_mean_combo$group.index))
        rr_mean_combo$mean.rr<-as.numeric(as.character(rr_mean_combo$mean.rr))
        rr_mean_combo$lcl<-as.numeric(as.character(rr_mean_combo$lcl))
        rr_mean_combo$ucl<-as.numeric(as.character(rr_mean_combo$ucl))
        rr_mean_combo$group.index[rr_mean_combo$Model==2]<-rr_mean_combo$group.index[rr_mean_combo$Model==2]+0.15
        rr_mean_combo$group.index[rr_mean_combo$Model==3]<-rr_mean_combo$group.index[rr_mean_combo$Model==3]+0.3
        rr_mean_combo$group.index[rr_mean_combo$Model==4]<-rr_mean_combo$group.index[rr_mean_combo$Model==4]+0.45
        rr_mean_combo$Model<-as.character(rr_mean_combo$Model)
        rr_mean_combo$Model[rr_mean_combo$Model=='1']<-"Synthetic Controls"
        rr_mean_combo$Model[rr_mean_combo$Model=='2']<-"Time trend"
        rr_mean_combo$Model[rr_mean_combo$Model=='3']<-"Time trend (No offset)"
        rr_mean_combo$Model[rr_mean_combo$Model=='4']<-"STL+PCA"
        cbPalette <- c("#1b9e77", "#d95f02", "#7570b3",'#e7298a')
        rr_mean_combo$est.index<-as.factor(1:nrow(rr_mean_combo))
        #Fix order for axis
        rr_mean_combo$Model<-as.factor(rr_mean_combo$Model)
        rr_mean_combo$Model = factor(rr_mean_combo$Model,levels(rr_mean_combo$Model)[c(2,3,4,1)])
        #print(levels(rr_mean_combo$Model))

cumsum_prevented <- sapply(groups, FUN = cumsum_func, quantiles = quantiles_full, simplify = 'array')
cumsum_prevented_pca <- sapply(groups, FUN = cumsum_func, quantiles = quantiles_pca, simplify = 'array')
cumsum_prevented_time <- sapply(groups, FUN = cumsum_func, quantiles = quantiles_time, simplify = 'array')
cumsum_prevented_best <- sapply(groups, FUN = cumsum_func, quantiles = quantiles_best, simplify = 'array')

save.best.est<-list(log_rr_sd_best,post_period,outcome_plot, time_points,ann_pred_quantiles_best, pred_quantiles_best,rr_roll_best,rr_mean_best,rr_mean_best_intervals,cumsum_prevented_best)
names(save.best.est)<-c('log_rr_sd_best','post_period','outcome_plot','time_points', 'ann_pred_quantiles_best', 'pred_quantiles_best','rr_roll_best','rr_mean_best','rr_mean_best_intervals','cumsum_prevented_best')
saveRDS(save.best.est, file=paste0(output_directory, country, "best estimates.rds"))

##Model size for SC model
model.size.sc<-sapply(impact_full,modelsize_func)

```

```{r sensitivity_analyses, include = FALSE}
if(sensitivity){
#Pred Sensitivity Analysis--tests effect of changing prior on Ncovars from 3 to 2 to 10
# cl <- makeCluster(n_cores)
# clusterEvalQ(cl, {library(CausalImpact, quietly = TRUE); library(lubridate, quietly = TRUE); library(RcppRoll, quietly = TRUE)})
# clusterExport(cl, c('doCausalImpact', 'predSensitivityAnalysis', 'inclusionProb', 'rrPredQuantiles', 'getPred', 'getRR', 'groups', 'ds', 'data_full', 'denom_name', 'outcome_mean', 'outcome_sd', 'intervention_date', 'eval_period', 'post_period', 'time_points', 'n_seasons'), environment())
# 
# sensitivity_analysis_pred_2  <- setNames(as.data.frame(t(parSapply(cl, groups, predSensitivityAnalysis, ds = ds, zoo_data = data_full, denom_name = denom_name, outcome_mean = outcome_mean, outcome_sd = outcome_sd, intervention_date = intervention_date, eval_period = eval_period, post_period = post_period, time_points = time_points, n_seasons = n_seasons, n_pred = 2 ))), c('Lower CI', 'Point Estimate', 'Upper CI'))
# sensitivity_analysis_pred_10 <- setNames(as.data.frame(t(parSapply(cl, groups, predSensitivityAnalysis, ds = ds, zoo_data = data_full, denom_name = denom_name, outcome_mean = outcome_mean, outcome_sd = outcome_sd, intervention_date = intervention_date, eval_period = eval_period, post_period = post_period, time_points = time_points, n_seasons = n_seasons, n_pred = 10))), c('Lower CI', 'Point Estimate', 'Upper CI'))
# 
# stopCluster(cl)
# 
# sensitivity_analysis_pred_2_intervals  <- data.frame('Estimate (95% CI)' = makeInterval(sensitivity_analysis_pred_2[, 2],  sensitivity_analysis_pred_2[, 3],  sensitivity_analysis_pred_2[, 1]),  row.names = groups, check.names = FALSE)
# sensitivity_analysis_pred_10_intervals <- data.frame('Estimate (95% CI)' = makeInterval(sensitivity_analysis_pred_10[, 2], sensitivity_analysis_pred_10[, 3], sensitivity_analysis_pred_10[, 1]), row.names = groups, check.names = FALSE)
# 


bad_sensitivity_groups <- sapply(covars_full, function (covar) {ncol(covar) <= n_seasons-1+3})
 sensitivity_covars_full <- covars_full[!bad_sensitivity_groups]
 sensitivity_ds <- ds[!bad_sensitivity_groups]
 sensitivity_impact_full <- impact_full[!bad_sensitivity_groups]
 sensitivity_groups <- groups[!bad_sensitivity_groups]

if (length(sensitivity_groups)!=0) {
 #Weight Sensitivity Analysis - top weighted variables are excluded and analysis is re-run.
cl <- makeCluster(n_cores)
clusterEvalQ(cl, {library(pogit, quietly = TRUE); library(lubridate, quietly = TRUE); library(RcppRoll, quietly = TRUE)})
clusterExport(cl, c('sensitivity_ds', 'doCausalImpact', 'year_def', 'weightSensitivityAnalysis', 'rrPredQuantiles', 'sensitivity_groups', 'intervention_date', 'outcome', 'time_points', 'n_seasons',  'eval_period', 'post_period','crossval'), environment())
  sensitivity_analysis_full <- setNames(parLapply(cl, sensitivity_groups, weightSensitivityAnalysis, covars = sensitivity_covars_full, ds = sensitivity_ds, impact = sensitivity_impact_full, time_points = time_points, intervention_date = intervention_date, n_seasons = n_seasons, outcome = outcome,  eval_period = eval_period, post_period = post_period), sensitivity_groups)
stopCluster(cl)

sensitivity_pred_quantiles  <- lapply(sensitivity_analysis_full, FUN = function(sensitivity_analysis) {
	pred_list <- vector(mode = 'list', length = length(sensitivity_analysis))
	for (sensitivity_index in 1:length(sensitivity_analysis)) {
		pred_list[[sensitivity_index]] <- getPred(sensitivity_analysis[[sensitivity_index]])
	}
	return(pred_list)
})

#Table of rate ratios for each sensitivity analysis level
sensitivity_table <- t(sapply(sensitivity_groups, sensitivityTable, sensitivity_analysis = sensitivity_analysis_full, original_rr = rr_mean_full))
sensitivity_table_intervals <- data.frame('Estimate (95% CI)' = makeInterval(sensitivity_table[, 2],  sensitivity_table[, 3],  sensitivity_table[, 1]),
																					'Top Control 1' = sensitivity_table[, 'Top Control 1'],
																					'Inclusion Probability of Control 1' = sensitivity_table[, 'Inclusion Probability of Control 1'],
																					'Control 1 Estimate (95% CI)' = makeInterval(sensitivity_table[, 7],  sensitivity_table[, 8],  sensitivity_table[, 6]),
																					'Top Control 2' = sensitivity_table[, 'Top Control 2'],
																					'Inclusion Probability of Control 2' = sensitivity_table[, 'Inclusion Probability of Control 2'],
																					'Control 2 Estimate (95% CI)' = makeInterval(sensitivity_table[, 12],  sensitivity_table[, 13],  sensitivity_table[, 11]),
																					'Top Control 3' = sensitivity_table[, 'Top Control 3'],
																					'Inclusion Probability of Control 3' = sensitivity_table[, 'Inclusion Probability of Control 3'],
																					'Control 3 Estimate (95% CI)' = makeInterval(sensitivity_table[, 17],  sensitivity_table[, 18],  sensitivity_table[, 16]), check.names = FALSE)
rr_table <- cbind.data.frame(round(rr_mean_time[!bad_sensitivity_groups, ],2), sensitivity_table)
rr_table_intervals <- cbind('Trend Estimate (95% CI)' = rr_mean_time_intervals[!bad_sensitivity_groups, ], sensitivity_table_intervals)
} else {
  sensitivity_table_intervals <- NA
}
}

```


#`r country` Results

```{r sparse}
if (!is.null(names(sparse_groups[sparse_groups])) && length(names(sparse_groups[sparse_groups])) != 0) {
	kable(data.frame('Sparse Groups' = names(sparse_groups[sparse_groups]), check.names = FALSE), align = 'c')
}
```

##combine estimates
```{r Comparison of estimates from different models}
if (crossval){
kable( cbind.data.frame(rr_mean_stack_intervals,rr_mean_full_intervals,rr_mean_time_intervals,rr_mean_time_no_offset_intervals,rr_mean_its_intervals, rr_mean_pca_intervals), align = 'c')
}else{
kable( cbind.data.frame(rr_mean_best_intervals,rr_mean_full_intervals,rr_mean_time_intervals,rr_mean_time_no_offset_intervals,rr_mean_its_intervals, rr_mean_pca_intervals), align = 'c')  
}
```

##Plot of Rate ratios, with size proportional to cross validation weights
```{r fig.width=5, fig.height=3, fig.align = "center", dpi=300, echo=FALSE}
#Compare rate ratios, with size of marker scaled to cross val weights
		ggplot(rr_mean_combo, aes(x=group.index, y=mean.rr, color=Model,group=Model)) + 
	  geom_errorbar(aes(ymin=lcl, ymax=ucl), colour="gray", width=.0) +
	  geom_point(aes(shape=Model, size=est.index))+
     scale_shape_manual(values=c(15, 16, 17,18))+
	  scale_size_manual(values=c(point.weights2$value*2)) + #Scales area, which is optimal for bubbl plot
	  #geom_errorbar(rr_mean_combo,aes(ymin=lcl, ymax=ucl), colour="black", width=.1) +
	  theme_bw() +
	  guides(size=FALSE)+ #turn off size axis
	  scale_colour_manual(values=cbPalette)+
	  labs(x = "Group", y="Rate ratio")+
	  geom_hline(yintercept = 1, colour='gray',linetype = 2)+
	  theme(axis.line = element_line(colour = "black"),
	        legend.position=c(0.2, 0.9),
	        panel.grid.major = element_blank(),
	        panel.grid.minor = element_blank(),
	        panel.border = element_blank(),
	        panel.background = element_blank()) 
```

##Weights for each of the models from cross validation
```{r Comparison of Cross validation Weights from different models}
if(crossval){
kable(stacking_weights.all, align = 'c')
} else{
      print("Cross-validation not performed")
    }
```
  
##Number of variables selected in SC analysis
```{r modelsize}
kable(model.size.sc, col.names=c('Model Size'))
```

##Inclusion Probabilities
```{r incl, include = FALSE}
incl_probs <- NULL
	for (group in groups) {
	    incl_prob=impact_full[[group]]$inclusion_probs[-c(1:(n_seasons-1)),]
	    incl_prob<- incl_prob[order(-incl_prob$inclusion_probs),]
	    incl_prob<-incl_prob[c(1:3),]
	    incl_prob2<-incl_prob[,2]
	    incl_prob_names=incl_prob[,1]
			incl_prob3 <- data.frame('Group' = group, 'Greatest Inclusion Variable' = incl_prob_names[1], 'Greatest Inclusion Probability' = incl_prob2[1], 'Second Greatest Inclusion Variable' = incl_prob_names[2], 'Second Greatest Inclusion Probability' = incl_prob2[2], 'Third Greatest Inclusion Variable' = incl_prob_names[3], 'Third Greatest Inclusion Probability' = incl_prob2[3], check.names = FALSE)
			incl_probs <- rbind(incl_probs, incl_prob3)
		}
rownames(incl_probs) <- NULL
```

```{r incl_table}
kable(incl_probs, align = 'c')
```

##Weight Sensitivity Analysis
```{r sensitivity}
if (exists('sensitivity_table_intervals')) {
kable(sensitivity_table_intervals, align = 'c')
}
```


##Plots
```{r plots,fig.height =3 , fig.width = 5, fig.align = "center", dpi=300,results = 'asis'}
source('./synthetic_control_plot.R', local=FALSE)
```

##Print results
```{r save_results, echo=FALSE}
source('./synthetic_control_write_results.R', local = FALSE)

```