---
author: "Daniel Weinberger"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Brazil example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
params:
  sensitivity: TRUE
  crossval: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

---

```{r setup_packages, include=FALSE}
library(knitr)
library(syncon)
```

---

```{r setup_data, include=FALSE}
data(pnas_brazil, package = "syncon")
analysis <- syncon.init(
  country = "Brazil", data = pnas_brazil,
  pre_period_start = "2004-01-01", pre_period_end = "2009-12-31",
  post_period_start = "2010-01-01", post_period_end = "2013-12-01",
  eval_period_start = "2012-01-01", eval_period_end = "2013-12-01",
  n_seasons = 12, year_def = "cal_year",
  group_name = "age_group", date_name = "date", outcome_name = "J12_18", denom_name = "ach_noj"
)
set.seed(1)
```

---
title: "Estimated change associated with the introduction of vaccine in `r analysis$country`"
---

```{r main analysis, include = FALSE}
impact_results = syncon.impact(analysis)
```

```{r crossval, include = FALSE}
if (params$crossval) {
  crossval_results <- syncon.crossval(analysis)
}
```

```{r sensitivity_analyses, include = FALSE}
if (params$sensitivity) {
  sensitivity_results <- syncon.sensitivity(analysis)
}
```


#`r params$country` Results

```{r sparse}
if (!is.null(names(analysis$sparse_groups[analysis$sparse_groups])) && length(names(analysis$sparse_groups[analysis$sparse_groups])) != 0) {
  kable(data.frame("Sparse Groups" = names(analysis$sparse_groups[analysis$sparse_groups]), check.names = FALSE), align = "c")
}
```

##combine estimates
```{r Comparison of estimates from different models}
if (params$crossval) {
  kable(cbind.data.frame(crossval_results$rr_mean_stack_intervals, impact_results$full$rr_mean_intervals, impact_results$time$rr_mean_intervals, impact_results$time_no_offset$rr_mean_intervals, impact_results$its$rr_mean_intervals, impact_results$pca$rr_mean_intervals), align = "c")
} else {
  kable(cbind.data.frame(impact_results$best$rr_mean_intervals, impact_results$full$rr_mean_intervals, impact_results$time$rr_mean_intervals, impact_results$time_no_offset$rr_mean_intervals, impact_results$its$rr_mean_intervals, impact_results$pca$rr_mean_intervals), align = "c")
}
```

##Plot of Rate ratios, with size proportional to cross validation weights
```{r fig.width=5, fig.height=3, fig.align = "center", dpi=300, echo=FALSE}
plots <- syncon.plots(analysis)
plots$summary
```

##Weights for each of the models from cross validation
```{r Comparison of Cross validation Weights from different models}
if (params$crossval) {
  kable(crossval_results$stacking_weights.all, align = "c")
} else {
  print("Cross-validation not performed")
}
```
  
##Number of variables selected in SC analysis
```{r modelsize}
kable(analysis$model_size, col.names = c("Model Size"))
```

##Inclusion Probabilities
```{r incl, include = FALSE}
incl_probs <- NULL
for (group in analysis$groups) {
  incl_prob <- impact_results$full$groups[[group]]$inclusion_probs[-c(1:(analysis$n_seasons - 1)), ]
  incl_prob <- incl_prob[order(-incl_prob$inclusion_probs), ]
  incl_prob <- incl_prob[c(1:3), ]
  incl_prob2 <- incl_prob[, 2]
  incl_prob_names <- incl_prob[, 1]
  incl_prob3 <- data.frame("Group" = group, "Greatest Inclusion Variable" = incl_prob_names[1], "Greatest Inclusion Probability" = incl_prob2[1], "Second Greatest Inclusion Variable" = incl_prob_names[2], "Second Greatest Inclusion Probability" = incl_prob2[2], "Third Greatest Inclusion Variable" = incl_prob_names[3], "Third Greatest Inclusion Probability" = incl_prob2[3], check.names = FALSE)
  incl_probs <- rbind(incl_probs, incl_prob3)
}
rownames(incl_probs) <- NULL
```

```{r incl_table}
kable(incl_probs, align = "c")
```

##Weight Sensitivity Analysis
```{r sensitivity}
if (exists("sensitivity_results")) {
  kable(sensitivity_results$sensitivity_table_intervals, align = "c")
}
```


##Plots
```{r plots,fig.height =3 , fig.width = 5, fig.align = "center", dpi=300,results = 'asis'}
for (group in names(plots$groups)) {
  for (group_plot in plots$groups[[group]]) {
    print(group_plot)
  }
}
```

##Print results
```{r save_results, echo=FALSE}
output_file <- "Results" # Directory where results will be saved.
output_file <- paste0(output_file, "_", analysis$country, "_", format(Sys.time(), "%Y-%m-%d-%H%M%S"), ".Rds")
syncon.save(analysis, output_file)
```
